### 2021-06-05 paper/report.tex
Add a couple of paragraphs.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity on many dimensions. The development of highly effective vaccines holds the promise of containment in the medium term. However, most countries find themselves many months---and often years---away from reaching vaccination-induced herd immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} In the meantime, it is of utmost importance to employ an effective mix of strategies for containing the virus. The most frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While this has allowed some countries to sustain equilibria with very low infection numbers\comment[id=HM]{Cite Priesemann paper or other}, most have seen large ups and downs in their infection rates. Containment measures have become increasingly diverse and included testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the influence of seasonal patterns or more infectious virus strains are well understood in quantitative terms. This paper develops a model incorporating all these factors. The framework allows to combine a wide variety of data in a timely fashion, making it useful to predict the effects of various interventions. We apply the model to Germany and show that rapid testing had the largest impact on the reduction in infections by XXX\% during the A weeks between X April and Y May.\comment[id=HM]{insert some useful numbers}

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?}, but the precise number is difficult to model.

At the starting point of our analysis, the

The \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}. The Figure~\ref{fig:stringency_index}

We describe the evolution of the pandemic and of its drivers in Figure~\ref{fig:pandemic_drivers_model_fit}. The black line in Figure~\ref{fig:aggregated_fit} shows the officially recorded cases;

We transform the index so that 1 represents the situation in mid-September and 0 represents that all restrictions incorporated in the index are in place. The six weeks between  was a steep rise in infections in

The setting in our analysis 
In late summer and early fall, restrictions were few. A distance of 1.5m had to be kept and masking requirements were enforced in public locations.\comment[id=HM]{pls double-check, add if I am missing important stuff}. 
 Figure~\ref{fig:stringency_index} Important to remember that multipliers are relative to that period

@@

@@

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity on many dimensions. The development of highly effective vaccines holds the promise of containment in the medium term. However, most countries find themselves many months---and often years---away from reaching vaccination-induced herd immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} In the meantime, it is of utmost importance to employ an effective mix of strategies for containing the virus. The most frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While this has allowed some countries to sustain equilibria with very low infection numbers\comment[id=HM]{Cite Priesemann paper or other}, most have seen large ups and downs in their infection rates. Containment measures have become increasingly diverse and included testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the influence of seasonal patterns or more infectious virus strains are well understood in quantitative terms. This paper develops a model incorporating all these factors. The framework allows to combine a wide variety of data in a timely fashion, making it useful to predict the effects of various interventions. We apply the model to Germany and show that rapid testing had the largest impact on the reduction in infections by XXX\% during the A weeks between X April and Y May.\comment[id=HM]{insert some useful numbers}. We conclude that rapid tests should play a large role...

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We model the period mid-September 2020 to the end of May 2020. We pick the starting date for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?}, but the precise number is difficult to model.

Figure~{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially recorded cases; the \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}, which tracks the tightness of non-pharmaceutical interventions. We transform the index so that lower values represent higher levels of restrictions. A value of zero means all measures incorporated in the index are turned on. The value 1 represents the situation of mid-September, where half of all restrictions incorporated in the index are active.\comment[id=HM]{Need to find version of index with a couple of measures, probably need the API access...}. In the six weeks between mid September and mid October, cases increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table somewhere?}. Restrictions were somewhat tightened in mid-October and again in early November. New infections remained constant throughout November, before rising again in December. In mid December, other lockdown. So far, traditional measures only

Starting in January,  becomes relevant.
\begin{itemize}
    \item Vaccines
    \item Tests
    \item Seasonality March onwards.
    \item B.1.1.7 February onwards
\end{itemize}

Our model:
\begin{itemize}
    \item Fit is great
    \item Multipliers for three categories (how calculated precisely, refer to appendix for breakdown)
    \item Tests fit well
    \item Share known cases, how calculated
\end{itemize}

@@

Reassured by good fit and a couple of external checks (fall vacation regression?), we consider the relative effects of different measures in 2021
\begin{itemize}
    \item Rapid tests, 
    \item seasonality
    \item vaccines
\end{itemize}

lessons learned

@@

Schooling very contentious. Likely damage to child development.

We show

Screening effect: ...
